---
title: "plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Setup
Loading the data

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(leaflet)
```

```{r}
data("nyc_airbnb")

nyc_airbnb_1 =
  nyc_airbnb %>% 
    mutate(rating = review_scores_location / 2) %>% 
    select(neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>% 
  filter(neighbourhood_group == "Manhattan",
         price %in% 100:500,
         room_type == "Entire home/apt") %>% 
  drop_na(rating)
```

# Plotly plots

## Scatterplot

\n puts stuff on the next line
str_c has created a new variable with those columns

Plotly works and looks like ggplot that requires the aesthetics to work.  

```{r}
nyc_airbnb_1 %>% 
  mutate(
    text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% 
  plot_ly(x = ~lat, y = ~long, color = ~price, text = ~text_label, alpha = 0.5, type = "scatter", mode = "markers")
```

## Boxplot

```{r}
nyc_airbnb_1 %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, x = ~neighbourhood, color = ~neighbourhood,
          type = "box", colors = "viridis")
```

## Barplot

```{r}
nyc_airbnb_1 %>% 
  count(neighbourhood) %>% 
  mutate(
    neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```

# ggplotly

```{r}
ggp_scatter =
  nyc_airbnb_1 %>% 
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point()

ggplotly(ggp_scatter)
```

## Boxplots
fct_reorder considers two variables and organizes the data in those two variables.

Boxplots
```{r}
nyc_airbnb_1 %>% 
  filter(
    price <1000,
    neighbourhood_group == "Manhattan") %>% 
  mutate(
    neighbourhood = fct_reorder(neighbourhood, price)) %>%
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()
```

## Map
All of NYC 
```{r}
nyc_airbnb_2 =
  nyc_airbnb %>% 
    mutate(rating = review_scores_location / 2) %>% 
    select(neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>% 
  filter(price %in% 100:500,
         room_type == "Entire home/apt") %>% 
  drop_na(rating) 
```

Sample of 1000 Airbnbs
```{r}
nyc_airbnb_2 %>% 
  sample_n(10) %>% 
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point()
```

Generate Leaflet map
```{r}
nyc_airbnb_2 %>% 
leaflet() %>% 
  addProviderTiles(providers$Stamen.Toner) %>% 
  addMarkers(~lat, ~long, popup = ~ rating)
```

